---
title: "DSCI445 - Homework 1"
author: "Your Name"
date: "Due 9/11/2019 by 4pm"
output: pdf_document
---

Be sure to `set.seed(400)` at the beginning of your homework. 

```{r}
#reproducibility
set.seed(400)
```

## R & ggplot2

```{r}
## load the data
library(ggplot2)

## take a look
head(diamonds)

#################################
## Continue your analysis here ##
#################################
```


## Regression

```{r}
## load the data
library(MASS)

## take a look
head(Boston)
```

Start by visually inspecting the data to get an idea of relationships that might be present (**hint:** look into the `ggpairs` function in the `GGally` package.). Describe what you see.

```{r}
## from the hint
library(GGally)

## make plots and describe
```

Next fit linear models using the `lm()` function:

(a) For each predictor fit a simple linear regression model to predict the response. Describe your results. In which of the models is there a statistically significant association between the predictor and the response?

(b) Fit a multiple regression model to predict the response using all of the predictors. Describe your results (including diagnostic plots). For which predictors can we reject the null hypothesis $H_0: \beta_j = 0$?

(c) How do your results from (a) compare to your results from (b)? Create a plot displaying the univariate regression coefficients from (a) on the $x$-axis and the multiple regression coefficients from (b) on the $y$-axis. That is, each predictor is displayed as a single point on the plot. Its coefficient in a simple linear regression model is shown as its $x$ coordinate and its coefficient in a multiple linear regression model is shown as its $y$ coordinate. Describe what you see.

 
Turn in in a pdf of your analysis to canvas using the provided Rmd file as a template. Your Rmd file on rstudio.cloud will also be used in grading, so be sure they are identical.

